Effort and Delay Discounting in a Foraging Environment

### 2019-04-25 Cost2/Cost2_prereg_remake.Rmd
block-wise prop accepted plot

dataAll <- data_frame(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))

@@

# Another approach
# This will just plot the density of the completed trials before/after, trying to get at the possible fatigue experienced in the physical effort condition.
# Response patterns for each subject look pretty similar, with adequate optimality adaptation.
#
# for (i in 1:nSubs){
# plot(density(which(physBefore[[i]]$Choice==1)),
#      main = paste("Choices in time, before and after for subject:",i),
#      xlab = "Trials (completed)")
# lines(density(which(physAfter[[i]]$Choice==1)), col = "red")
# }
```

>>>>

dataAll <- data_frame(SubjID = files) %>%
  mutate(contents = map(SubjID, ~ read_csv(., col_types = cols())))  %>%
  mutate(Cost = substring(SubjID, 5, 8),
         Cost = case_when(Cost == "wait" ~ "Wait",
                          Cost == "cogT" ~ "Cognitive",
                          Cost == "phys" ~ "Physical",
                          Cost == "phea" ~ "Easy"),
         Cost = factor(Cost, levels = c("Physical", "Cognitive", "Wait", "Easy")),
         SubjID = substring(SubjID, 0, 3)) %>%
  unnest() %>%
  mutate(Half = ifelse(Block < 4, "Half_1", "Half_2"))

@@

# dataAll %>%
#   filter(Choice < 2) %>%
#   group_by(SubjID) %>%
#   #mutate(Block = do.call(c, lapply(c(2,4,6), function(x) {rep(x/2, sum(Block %in% c(x-1, x)))}))) %>%
#   group_by(SubjID, Cost, Block) %>%
#   summarise(propAccept_subj = mean(Choice)) %>%
#   group_by(Cost, Block) %>%
#   summarize(propAccept = mean(propAccept_subj),
#             seAccept = sd(propAccept_subj)/sqrt(nSubjs)) %>%
#   ggplot(aes(Block, propAccept, fill = Cost)) +
#     geom_point(size = 2, pch = 21, color = "black") +
#     geom_errorbar(aes(ymin=propAccept - seAccept, ymax=propAccept + seAccept, color = Cost), width = 0.1) +
#     geom_line(aes(color = Cost)) +
#     ylim(0.5, 1) +
#     scale_x_continuous(breaks = seq(6)) +
#     scale_color_manual(values = cols) +
#     scale_fill_manual(values = cols) +
#     theme_classic()
```
